Paper

### 2021-10-12 draft_paper.Rmd
broke down domestic by grade but nothing new

# read in forecasts
# path to UoM server different for everyone
call_forecasts <- read_rds("/Volumes/n8_covid/call_forecasts.Rds")
all_rt_forecast <- read_rds("/Volumes/n8_covid/all_resp_time_forecast.Rds")
by_type_rt_forecast <- read_rds("/Volumes/n8_covid/by_type_rt_forecasts.Rds")
by_grade_rt_forecast <- read_rds("/Volumes/n8_covid/by_grade_rt_forecasts.Rds")
all_calls_attended_forecast <- read_rds("/Volumes/n8_covid/all_attended_forecasts.Rds")
by_type_attended_forecast <- read_rds("/Volumes/n8_covid/by_type_attended_forecasts.Rds")

@@

  # conditionally label y axis
  y_axis_label <- case_when(df_name %in% c("by_type_rt_forecast", 
                                           "by_grade_rt_forecast") ~ "Median response time (in minutes)", 
                         df_name %in% c("call_forecasts") ~ "Weekly count of calls for service", 
                         df_name %in% c("by_type_attended_forecast", "by_grade_attended_forecast") ~ "Weekly % of calls attended")

  # conditionally find actual value column
  actual_col_name <- case_when(df_name %in% c("by_type_rt_forecast", 
                                           "by_grade_rt_forecast") ~ "actual_rt", 
                         df_name %in% c("call_forecasts") ~ "actual_calls", 
                         df_name %in% c("by_type_attended_forecast", "by_grade_attended_forecast") ~ "actual_attended")

  forecasts %>% 
    filter(eval(as.symbol(variable)) == value) %>% 
    # Occasionally the ARIMA model may produce forecast confidence intervals
    # that are less than zero, which will not show up on the plot because we
    # have set the y axis to start at zero (to make changes in vertical position
    # on the axis representative of changes in magnitude). To deal with this we
    # will manually set the lower CI of the forecasts to be zero if it is less
    # than zero in the original forecast.
    mutate(forecast_lower = ifelse(forecast_lower < 0, 0, forecast_lower)) %>% 
    ggplot() +
    # Forecast
    geom_ribbon(
      aes(incident_week, ymin = forecast_lower, ymax = forecast_upper), 
      na.rm = TRUE,
      alpha = 0.5, 
      fill = "grey80"
    ) +
    geom_line(aes(incident_week, forecast_mean), na.rm = TRUE, linetype = "22") +
    # Dates of interest
    geom_vline(aes(xintercept = date), data = dates, linetype = "12") +
    geom_label(aes(date, 0, label = row), data = dates, colour = "grey20") +
    # Actual calls
    geom_line(aes(incident_week, eval(as.symbol(actual_col_name)))) +
    geom_point(aes(incident_week, eval(as.symbol(actual_col_name)), fill = sig), shape = 21) +
    scale_x_date(date_labels = "%e %b\n%Y", 
                 limits = as.Date(c("2020-01-06", "2020-12-21")))+
    scale_y_continuous(limits = c(0, NA), labels = scales::comma_format()) +
    scale_fill_manual(values = c(`TRUE` = "black", `FALSE` = "grey80")) +
    labs(
      title = value,
      subtitle = "",
      caption = "Forecast calculated using data up to 31 January 2020",
      x = NULL,
      y = y_axis_label,
      fill = "Actual response time significantly different from forecast"
    ) +
    theme_minimal() +
    theme(legend.position = "bottom", plot.title = element_text(face = "bold"))

@@

@@

Police response by grade

@@

# Attended by grade fig and response time by grade fig

>>>>

# read in forecasts
# path to UoM server different for everyone
call_forecasts <- read_rds("/Volumes/n8_covid/call_forecasts.Rds")
all_rt_forecast <- read_rds("/Volumes/n8_covid/all_resp_time_forecast.Rds")
by_type_rt_forecast <- read_rds("/Volumes/n8_covid/by_type_rt_forecasts.Rds")
by_grade_rt_forecast <- read_rds("/Volumes/n8_covid/by_grade_rt_forecasts.Rds")
all_calls_attended_forecast <- read_rds("/Volumes/n8_covid/all_attended_forecasts.Rds")
by_type_attended_forecast <- read_rds("/Volumes/n8_covid/by_type_attended_forecasts.Rds")
domestic_by_grade_volume_forecasts <- read_rds("/Volumes/n8_covid/domestic_by_grade_volume_forecasts.Rds")
domestic_by_grade_rt_forecast <- read_rds("/Volumes/n8_covid/domestic_by_grade_rt_forecasts.Rds")

@@

  # conditionally label y axis
  y_axis_label <- case_when(df_name %in% c("by_type_rt_forecast", 
                                           "by_grade_rt_forecast", 
                                           "domestic_by_grade_rt_forecast", 
                                           "domestic_by_grade_volume_forecasts") ~ "Median response time (in minutes)", 
                         df_name %in% c("call_forecasts") ~ "Weekly count of calls for service", 
                         df_name %in% c("by_type_attended_forecast", "by_grade_attended_forecast") ~ "Weekly % of calls attended")

  # conditionally find actual value column
  actual_col_name <- case_when(df_name %in% c("by_type_rt_forecast", 
                                           "by_grade_rt_forecast",
                                           "domestic_by_grade_rt_forecast", 
                                           "domestic_by_grade_volume_forecasts") ~ "actual_rt", 
                         df_name %in% c("call_forecasts") ~ "actual_calls", 
                         df_name %in% c("by_type_attended_forecast",
                                        "by_grade_attended_forecast") ~ "actual_attended")

  forecasts %>% 
    filter(eval(as.symbol(variable)) == value) %>% 
    # Occasionally the ARIMA model may produce forecast confidence intervals
    # that are less than zero, which will not show up on the plot because we
    # have set the y axis to start at zero (to make changes in vertical position
    # on the axis representative of changes in magnitude). To deal with this we
    # will manually set the lower CI of the forecasts to be zero if it is less
    # than zero in the original forecast.
    mutate(forecast_lower = ifelse(forecast_lower < 0, 0, forecast_lower)) %>% 
    ggplot() +
    # Forecast
    geom_ribbon(
      aes(incident_week, ymin = forecast_lower, ymax = forecast_upper), 
      na.rm = TRUE,
      alpha = 0.5, 
      fill = "grey80"
    ) +
    geom_line(aes(incident_week, forecast_mean), na.rm = TRUE, linetype = "22") +
    # Dates of interest
    geom_vline(aes(xintercept = date), data = dates, linetype = "12") +
    geom_label(aes(date, 0, label = row), data = dates, colour = "grey20") +
    # Actual calls
    geom_line(aes(incident_week, eval(as.symbol(actual_col_name)))) +
    geom_point(aes(incident_week, eval(as.symbol(actual_col_name)), fill = sig), shape = 21) +
    scale_x_date(date_labels = "%e %b\n%Y", 
                 limits = as.Date(c("2020-01-06", "2020-12-21")))+
    scale_y_continuous(limits = c(0, NA), labels = scales::comma_format()) +
    scale_fill_manual(values = c(`TRUE` = "black", `FALSE` = "grey80")) +
    labs(
      title = value,
      subtitle = "",
      caption = "Forecast calculated using data up to 31 January 2020",
      x = NULL,
      y = y_axis_label,
      fill = "Actual observed value significantly different from forecast"
    ) +
    theme_minimal() +
    theme(legend.position = "bottom", plot.title = element_text(face = "bold"))

@@

forecast_chart(domestic_by_grade_rt_forecast,"initial_grade_of_response", "Grade 1")

@@

@@

# Attended by grade fig

Police response by grade. For grade 1, response time was within what was forecasted, however for grade 2 calls response times decreased during the pandemic. For grades 3 and 4 the forecase is too noisy (too few observations).

```{r dvresponsebygrade}

# Response time by grade fig

forecast_chart(domestic_by_grade_rt_forecast,"initial_grade_of_response", "Grade 1")
forecast_chart(domestic_by_grade_rt_forecast,"initial_grade_of_response", "Grade 2")
